\subsection{Criteria Matching Operators}
\subsubsection{String Operators}
\label{sub:DerpOperators}
\begin{itemize}
\item with the exact - String comparison equality operator. Includes results where the specified field is an exact match for the provided string.
\item like - String comparison fuzzy equality operator. Includes results where the specified field is an approximate match for the provided string.
\item in the - Sub-String comparison equality operator. Includes results where a sub-string of the specified field is an exact match for the provided string.
\end{itemize}
\subsubsection{Datetime Operators}
\begin{itemize}
\item Date on - Date comparison equality operator. Includes results where the specified field is exactly the same date as the provided date.
\item date after - Date comparison greater-than operator. Includes results where the specified field is strictly after the provided date.
\item date before - Date comparison less-than operator. Includes results where the specified field is strictly before the provided date.
\end{itemize}
\subsubsection{Boolean Operators}
\begin{itemize}
\item which are $|$ are - Boolean comparison equality operator. Includes results where the specified field contains the boolean value of `true'.
\item which are not $|$ are not - Boolean comparison non-equality operator. Includes results where the specified field contains the boolean value of `false'.
\end{itemize}
\subsubsection{Numeric Operators}
\begin{itemize}
\item with exactly $|$ exactly - Number comparison equality operator. Includes results where the specified field contains the same numeric value as the provided numeric value.
\item with over $|$ over - Number comparison greater-than operator. Includes results where the specified field contains a value strictly greater than the provided numeric value.
\item with under $|$ under - Number comparison less-than operator. Includes results where the specified field contains a value strictly less than the provided numeric value.
\item with roughly $|$ roughly - Number comparison epsilon equality operator. Includes results where the specified field contains a value within an epsilon value greater or less than the provided numeric value.
\end{itemize}
\subsubsection{Misc Operators}
\begin{itemize}
\item matching - Criteria composition operator. The criteria corresponding to the provided name will be textually included into the current criteria or selection.
\item on - Substring search on "topical" fields as defined by a source module.
\item and $|$ or - Combine the results from the statements on either side of the operator.
\end{itemize}

\subsection{Selection Matching Operators}
\begin{itemize}
    \item from - Source selection operator/ Selection composition operator. Pulls posts from a registered source or a previously saved selection. 
    \item All criteria matching operators.
\end{itemize}

\subsection{Keywords}

\subsubsection{Main Mode}
\begin{itemize}
\item exit - Exits the program, and may only be used in the mode selection mode.
\item clear - Deletes a specified selection or criteria.
\item load/ unload - Loads a news source module or a knowledge module.
\item recall - Read out the selection statements or criteria statements which make up a specified selection or criterion.
\item read - Execute the specified selection and present the results.
\item create - Creates a new selection or criterion. Enters the respective builder mode.
\end{itemize}

\subsubsection{Selection and Criteria Builder Mode}
\begin{itemize}
\item stop - End mode keyword. Ends selection or criteria creation mode and clears the active state.
\item clear - Reset mode state keyword. Without leaving the current creation mode, clears the active state.
\item recall - Read out the selection statements or criteria statements which make up the object that is currently being built.
\item read - (selection builder only) Execute the selection currently being built and present the results.
\item save as - Store the current selection or criteria with a specified name. A saved selection or criteria may be used in the creation of other selections and criteria.
\item add - Select posts which match a set of criteria. \texttt{From} is disallowed in in add statements in the criteria builder mode.
\item remove - Remove posts which match a set of criteria.
\end{itemize}
