\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Scratchwork}

\begin{document}

\maketitle
\section{Initial Outline}
\begin{itemize}
    \item Domain of Application: Filtering Web Posts (Mainly News)
    \item Programming Paradigm: Declarative
    \item Program Structure: Textual, Natural English
    \item Memory Management: Automatic
    \item Data Types: 
    \begin{itemize}
        \item Posting
        \item String
        \item Boolean
        \item Number
        \item DateTime
        \item List
    \end{itemize}
    \item Expressions:
    \begin{itemize}
        \item (Find) (News articles) (on) (Reddit) (containing information) (on) (whales)
    \end{itemize}
    \item Variables:
    \begin{itemize}
        \item 
    \end{itemize}
\end{itemize}

\section{Problem Statement}

\subsection{DERP, Sept. 9, Logan Lembke}
It would be handy to hear the news on topics I care about as I head to school.

It can be hard to be specific when asking alexa/Siri/etc. to find information on the web about something. 

We aim to design an application which provides users a powerful interface for searching the web with natural English. 

\subsection{DERP Query Language, Sept. 9, Logan Lembke}

In order to precisely describe queries executed by DERP, we must construct an easy to speak, structured query language. 


\section{Representation}
\subsection{Predicates, Sept. 9, Logan Lembke}
For reddit our predicates may be backed by:
\begin{itemize}
    \item String search on 
    \begin{itemize}
        \item Title
        \item Username
        \item Post Tags
        \item Content Title
        \item Content Author
        \item Content Body
    \end{itemize}
    \item Date Matching on
    \begin{itemize}
        \item Post Date
        \item Content Date
    \end{itemize}
    \item Top N in Reddit Sort Categories
    \begin{itemize}
        \item Hot
        \item Rising
        \item Top
        \item New
        \item Controversial
    \end{itemize}
    \item Approximate? Reddit Upvote Count
    \item Any logical combination of the above
\end{itemize}

Content searches can backed by https://mercury.postlight.com/web-parser/.

In general, each of these predicates are functions of a given Reddit Post and the Mercury Web API.

The backend representation should likely be a function which takes in a reddit post and returns a boolean. Then these functions could be composed and used to lazily filter a stream of reddit articles.

We could abstract the providers of predicate fields into modules.

\subsection{Understanding Modules, Sept. 9, Logan Lembke}
In order to parse out new pieces of information from posts, an understanding module may be loaded. 

For instance a module could be defined for the mercury api.


\end{document}