\documentclass{article}
\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{comment}

\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{upquote}
\usepackage{listings}
\lstset{upquote=true,
frame=single,
breaklines=true,
postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
aboveskip=20pt,belowskip=20pt,}

\usepackage{bold-extra}
\usepackage{soul}
\usepackage{titlesec}       % Lines under Sections
\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]

\usepackage{etoolbox}       % Because titlesec removes section numbering -\_-
\makeatletter
\patchcmd{\ttlh@hang}{\parindent\z@}{\parindent\z@\leavevmode}{}{}
\patchcmd{\ttlh@hang}{\noindent}{}{}{}
\makeatother

\usepackage[T1]{fontenc}
\usepackage[scaled]{beramono}
\usepackage{calc}

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\ecode}[1]{\textit{\code{#1}}}
\newcommand{\bcode}[1]{\textbf{\code{#1}}}

\newcommand{\terminal}[1]{\code{#1}}
\newcommand{\nonterminal}[1]{\ecode{#1}}
\newcommand{\bnf}[1]{\bcode{#1}}

%\renewcommand\maketitle{}

% Give Table of Contents Hyperlinks
\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=blue
}
\pagenumbering{gobble}
% \pagenumbering{roman} % set the numbering style to lowercase letter\autoref*{#1}
\newcommand*{\fullref}[1]{\hyperref[{#1}]{section \ref*{#1} \nameref*{#1} }}
\title{\textbf{Dictation Evaluation Reddit Parser}}

\author{
Garcia, Benjamin \and
Lembke, Logan \and
Smith, Christopher \and
Stelter, Andrew
}
\date{September 21, 2018}


%\setcounter{secnumdepth}{4}

\titleformat{\paragraph}
{\normalfont\normalsize\bfseries}{\theparagraph}{1em}{}
\titlespacing*{\paragraph}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}


\usepackage{enumitem}
\newlength\onelen
\newlength\twolen

\setlength\onelen{3.5cm}
\setlength\twolen{1cm}
\newcommand{\myitem}[2]{%
  \item[\texttt{#1}] \makebox[\twolen][l]{\texttt{#2}}%
  }

\begin{document}

\addcontentsline{toc}{section}{Title}
\maketitle %%TODO: maketitle doesn't seem to be working

\newpage
\tableofcontents
% \addcontentsline{toc}{section}{Table of Contents}

\pagenumbering{roman}   % Set TOC page numbering to lowercase roman numerals



%%%%%%%%%%%%%%%%%%%%%%%%%%%% INTRO SECTION %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
% \hypersetup{
%     citecolor=blue,
%     filecolor=black,
%     linkcolor=blue,
%     urlcolor=blue
% }
\pagenumbering{arabic}  % Set content page numbering to arabic numerals


\part{Language Tutorial}
\section{Introduction}
This tutorial aims to quickly teach those skilled in the art how to use DERP to find, filter, and consume internet content. DERP is a Domain Specific Language (DSL) suited to information retrieval using natural English. For the purpose of this tutorial we will assume the existence of a ‘Reddit’ submodule which allows for retrieving data from www.reddit.com.

\subsection{Target Systems}
DERP is written in python 3. As such, DERP will run wherever python 3 is available. The DERP language is intended to be adapted to multiple platforms such as smart home devices, desktop computers, and mobile phones. However, this document specifically covers the desktop implementation of DERP. Most modules, such as the Reddit module, additionally require internet access.
\input{getting_started.tex}
\input{basic_usage.tex}
\input{qualifiers.tex}
\input{reusing_selections.tex}

\part{Refrence Guide}
This section describes the DERP language, as outlined in the DERP Language white paper submitted
to the course CSC 792 (Compilers) at the South Dakota School of Mines \& Technology in the Fall
of 2018. This reference defines all of the main constructs of the language and gives some examples
of their usages; it will not contain hard definitions of any of the specific language constructs
defined in plugins to the language; however, it may use some as examples.
\setlist[description]{font=\normalfont}
\input{syntax_notation.tex}
\input{language_extension.tex}
\input{lexical_conventions.tex}
\input{language_modes.tex}
\input{data_types.tex}
\input{statements_expressions.tex}
\end{document}
